---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oscarr

<!-- badges: start -->

<!-- badges: end -->

The goal of `oscarr` is to provide an R wrapper to [pyoscar](https://github.com/wmo-cop/pyoscar "https://github.com/wmo-cop/pyoscar") python module that provide an easy access to WMO OSCAR REST API. In other words, the package `oscarr` brings [pyoscar](https://github.com/wmo-cop/pyoscar "https://github.com/wmo-cop/pyoscar") to R Community.

# Installation

You can install the development version of oscarr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("oousmane/oscarr")
```

The following code set up an virtual environment for python dependencies

``` r
# environment path (replace if you needed)
my_env <- "~/.virtualenvs/pkg-oscarr/" # on Win system can be "C:/.virtualenvs/pkg-oscarr/"
# run this (works on macOS)
args <- paste("-m venv", my_env) 
system2("python3", args) # create environment
reticulate::use_virtualenv(my_env) # force reticulate to use my_env
# install pyoscar in environment
oscarr::install_pyoscar(my_env)
```

# Example

This is a basic example which shows you how to use `oscarr`:

```{r example}
library(oscarr)
# retrieve all oscar station within  a country get_stations(country="NGA") 
# Retrieve WMO OSCAR Station within Nigeria
# station report summary by using WIGOS identifier

wigos_baraboule <- "0-854-0-109"
get_station_report(identifier = wigos_baraboule)

```

You can add further constrains to the query

```{r}
## Add further constrains to station query
get_stations(program = "GBON",country = "BFA", station_type = "landFixed")
```
